Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-08-13 iced-2013/paper.tex
ICED survey methodology draft.

% Authors names
\author{\IEEEauthorblockN{Jordan Ell}
\IEEEauthorblockA{University of Victoria,
Victoria, British Columbia, Canada \\ jell@uvic.ca}
}

\author{\IEEEauthorblockN{Daniela Damian}
\IEEEauthorblockA{University of Victoria,
Victoria, British Columbia, Canada \\ danielad@csc.uvic.ca}
}

@@

We selected our participants from a large breadth of both open and closed source software development companies
and projects. The population which participated in our interview came from the following software groups: 
IBM, Mozilla, The GNOME Project, Microsoft Corporation, Subnet Solutions, Ruboss Technology Corporation, 
Amazon, Exporq Oy, Kano Apps, Fireworks Design, James Evans and Associates, and Frost Tree Games. 
Our participants we chosen based on their direct involvement in the actual writing of software for
their respective companies or projects. These participants' software development titles included: senior developer,
lead developer, software developer, software developer in test, and junior developer.
In addition to software development, some participants were also chosen based on their previous experience
of software development as well as their current experience with project management at some capacity. These management
type participants involved in project planning to some capacity between technical architecture, project maintainer,  
chief technical officer, or program manager.

@@

@@

\bibliographystyle{IEEEtran}
\balance
\bibliography{paper}

>>>>

\author{\IEEEauthorblockN{Jordan Ell}
\IEEEauthorblockA{University of Victoria,
Victoria, Canada \\ jell@uvic.ca}
IEEEauthorblockN{Daniela Damian}
\IEEEauthorblockA{University of Victoria,
Victoria, Canada \\ danielad@csc.uvic.ca}
}

@@

We selected our interview participants from a large breadth of both open and closed source software development companies
and projects. The population which participated in our interview came from the following software groups: 
IBM, Mozilla, The GNOME Project, Microsoft Corporation, Subnet Solutions, Ruboss Technology Corporation, 
Amazon, Exporq Oy, Kano Apps, Fireworks Design, James Evans and Associates, and Frost Tree Games. 
Our participants we chosen based on their direct involvement in the actual writing of software for
their respective companies or projects. These participants' software development titles included: senior developer,
lead developer, software developer, software developer in test, and junior developer.
In addition to software development, some participants were also chosen based on their previous experience
of software development as well as their current experience with project management at some capacity. These management
type participants involved in project planning to some capacity between technical architecture, project maintainer,  
chief technical officer, or program manager.

@@

\subsection{Survey Participants}

We selected our survey participants from a similar breadth of open and closed source software development 
companies and projects as the interviews participants with two large exceptions. The software organizations
that remained the same between interview and survey were: Mozilla, The GNOME Project, Microsoft Corporation, 
Subnet Solutions, Ruboss Technology Corporation, Amazon, Kano Apps, Fireworks Design, and Frost Tree Games.
However, participants who took part in the round of interviews were not asked to participate in the surveys but
rather to act as a contact point for other developers in their team, project, or organization who may be interested
in completing the survey. Aside from this aforementioned list, two large groups of developers were asked to
participate as well, these being GitHub users as well as Apache Software Foundation (Apache) developers. The GitHub
users were selected based on their large amounts of development activity on GitHub and the Apache developers
were selected based on their software development participation on specific projects known to be used heavily
by other organizations and projects.

\subsection{Survey Procedure}

The created survey was based off of the 12 categorical hypotheses given by the round of interviews. The survey
was designed to test these hypotheses and to acquire a larger sample size of developers who may have similar
or different opinions from those already acquired from the interviews. The survey went through two rounds of
piloting. Each pilot round consisted of five participants, who were previously interviewed, completing the survey
with feedback given at the end. The previous interview participants were selected based on their domain knowledge
expertise with indirect conflicts in order to provide what we think would be amount to better feedback and resulting
in a more polished survey. The final survey consisted of 2 multiple choice, 3 level of agreement,
6 level of use, and 9 short answer questions. Each non demographic question was made optional as it was shown 
through the interviews that some questions require more experience from participants than may be provided.

Survey participants were invited to participate in the survey by email. No reminder email was ever sent as the
survey responses were not connected with the invitation email addresses and thus participants who did respond
could not be removed from a reminder list. We directly emailed 1300 participants and ended with 78 responses
giving a response rate of 6\%. We attribute the low response rate with a couple of factors. One, the surveys
were conducted during the months of July and August while many participants may be away from their regular positions.
Two, our GitHub and Apache participants could not be verified as to whether or not they actively support the
email addresses used in the invitations. And finally, the survey was considered by some to be long and require
more development experience than may have been typical of some of those invited to participate.

After the survey was closed, preliminary analysis was applied to the short answer questions in the same manor
as the interview responses. We extracted a list of answers, opinions, and experiences for each of the 9 short
answer question fields while combining commonly mentioned answers where possible. The results again from this
preliminary analysis is a list of common and unique hypotheses to each of the 9 short answer questions.

@@

%\bibliographystyle{IEEEtran}
%\balance
%\bibliography{paper}
